Age-related changes in plant growth and traits

### 2015-09-01 RA_figs.rmd
Continued little fixes to main files (Growth_figs, RA_figs) - they now run in Knitr again
Some additional work in RA_figs, incorporating what we talked about in lab meeting last Thursday

@@

###RV curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_inv"
xvar <- "total_weight"

@@

mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

###Vegetative invesment by size curves by species, only including reproducing individuals  
* colored by age, but legend not correct, because "age 1" color used for youngest age with reproducing individuals

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

###Calculating cost of reproduction as a growth deficit
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
  plot
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

data <- subset(SummaryInd,repro_inv=0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results_cost <- summarise_all_fits(lmfits)

@@

plot(cost_ratio~RA,Summary2,col=col.spp(species),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
mod <- lm(RA~log(cost_ratio),data=subset(Summary2,RA>0))
words.bottom.left.logy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(cost_ratio~RA,Summary2,col=col.age(age),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
  plot
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost_ratio"
xvar <- "RA"

data <- subset(Summary2,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  }

mtext("ratio of predicted growth to actual growth", 2, outer=TRUE,cex=1.2)
mtext("RA", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost"
xvar <- "repro_inv"

data <- subset(Summary2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  abline(0,1)                  
}

@@

####There is a much less clearcut pattern with respect to height growth - for most species height growth declines dramatically with age, overshadowing any reprodutive maturity affects  
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_height"
xvar <- "height"

@@

mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_height"
xvar <- "height"

@@

mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
legend("bottomleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                        main=spp,col=col.age(data[[spp]]$age)
}

mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
legend("bottomleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
SummaryIndPCA <- SummaryInd %>%
  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
  select(prop_maxH,height,maxH,wood_density,LMA,seed_size,growth_leaf,
         growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)

SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
SummaryIndPCA$height <- log(SummaryIndPCA$height)
SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
SummaryIndPCA$growth_shoot_diameter <- log(SummaryIndPCA$growth_shoot_diameter+.001)
SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
SummaryIndPCA$growth_stem_diameter <- log(SummaryIndPCA$growth_stem_diameter)
SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
SummaryIndPCA$scaled_growth_stem_diameter <- log(SummaryIndPCA$scaled_growth_stem_diameter)
SummaryIndPCA$RA <- asin(sqrt(SummaryIndPCA$RA))

@@

PCA_scores <- as.data.frame(PCA_mod$x)
PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0)
SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)

@@

plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC1_scale
se1 <- PCA_by_species$PC1_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)

@@

plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_age$PC1_scale
se1 <- PCA_by_age$PC1_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC2_scale
se1 <- PCA_by_species$PC2_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)

@@

plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_age$PC2_scale
se1 <- PCA_by_age$PC2_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC3_scale
se1 <- PCA_by_species$PC3_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC3_scale
se1 <- PCA_by_age$PC3_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC4_scale
se1 <- PCA_by_species$PC4_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC4_scale
se1 <- PCA_by_age$PC4_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

>>>>

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

source("R/figures.R")
```

@@

###RV curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_inv"
xvar <- "total_weight_0"

@@

mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

###Vegetative invesment by size curves by species, only including reproducing individuals  
* colored by age

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight_0"

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight_0"

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "leaf_area_0"

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_inv"
xvar <- "leaf_area_0"

data <- subset(SummaryInd,repro_inv>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_inv"
xvar <- "leaf_area_0"

mtext("Total investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=15, fig.height=15}
par(mfcol=c(3,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,1,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "leaf_area_0"

yvar2 <- "repro_inv"
xvar2 <- "leaf_area_0"

yvar3 <- "total_inv"
xvar3 <- "leaf_area_0"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar3_vs_xvar3(data[[spp]], yvar3, xvar3,log="xy",xlab="",ylab="total invest (mg)",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  arrows(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,data[[spp]]$leaf_area_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="veg invest (mg)",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2,log="xy",xlab="",ylab="repro invest (mg)",cex=1.3,
                    col=col.age(data[[spp]]$age))
  #points(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,pch=1,cex=.8,col=col.age(data[[spp]]$age))
}

mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

###Calculating cost of reproduction as a growth deficit
    * despite having a clause to subset SummaryInd,
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

data_RA0 <- subset(SummaryInd,repro_inv==0&species!="BOLE")
data_RA0 <- split(data_RA0, data_RA0$species)
lmfits <- lapply(data_RA0, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results_cost <- summarise_all_fits(lmfits)

@@

plot(cost_ratio~repro_inv,Summary2,col=col.spp(species),pch=16,log="xy",ylab="ratio of predicted growth to actual growth")
mod <- lm(log(repro_inv)~log(cost_ratio),data=subset(Summary2,RA>0))
words.bottom.left.logxy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(cost_ratio~repro_inv,Summary2,col=col.age(age),pch=16,log="xy",ylab="ratio of predicted growth to actual growth")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost_ratio"
xvar <- "repro_inv"

data <- subset(Summary2,species!="BOLE")
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))              
}

@@

####There is a much less clearcut pattern with respect to height growth - for most species height growth declines dramatically with age, overshadowing any reprodutive maturity affects  
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_height"
xvar <- "height_0"

data <- subset(SummaryInd,growth_height>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant height (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_height"
xvar <- "height_0"

data <- subset(SummaryInd,growth_height>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant height (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
SummaryIndPCA <- SummaryInd %>%
  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
  select(prop_maxH,height_0,maxH,wood_density,LMA,seed_size,growth_leaf, growth_height,
         growth_stem_diameter,leaf_area_0,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight_0,
         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)

SummaryIndPCA$leaf_area_0 <- log((SummaryIndPCA$leaf_area_0)+.001)
SummaryIndPCA$total_weight_0 <- log(SummaryIndPCA$total_weight_0)
SummaryIndPCA$height_0 <- log(SummaryIndPCA$height_0)
SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
SummaryIndPCA$growth_shoot_diameter <- log(SummaryIndPCA$growth_shoot_diameter+.001)
SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
SummaryIndPCA$growth_stem_diameter <- log(SummaryIndPCA$growth_stem_diameter)
SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
SummaryIndPCA$scaled_growth_stem_diameter <- log(SummaryIndPCA$scaled_growth_stem_diameter)
SummaryIndPCA$RA <- asin(sqrt(SummaryIndPCA$RA))

  for(v in c("repro_all_count")) {
    i <- is.na(SummaryIndPCA[[v]])
    SummaryIndPCA[[v]][i] <- 0
  }

@@

PCA_scores <- as.data.frame(PCA_mod$x)
PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0,SummaryInd$shoot_leaf_area>0)
SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)

@@

plot(PC1_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC1_scale_mean
se1 <- PCA_by_species$PC1_scale_se
boxplot(PC1_scale_mean~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)

@@

plot(PC1_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age(age))
arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")

mean1 <- PCA_by_age$PC1_scale_mean
se1 <- PCA_by_age$PC1_scale_se
boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC2_scale_mean
se1 <- PCA_by_species$PC2_scale_se
boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)

@@

plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age))
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_age$PC2_scale_mean
se1 <- PCA_by_age$PC2_scale_se
boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC3_scale_mean
se1 <- PCA_by_species$PC3_scale_se
boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC3_scale_mean
se1 <- PCA_by_age$PC3_scale_se
boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC4_scale_mean
se1 <- PCA_by_species$PC4_scale_se
boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC4_scale_mean
se1 <- PCA_by_age$PC4_scale_se
boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```
